### 2022-10-26 manuscript.tex
Fixing citations [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/3096a8deace92d7df98c206c233bcf3f62c7e805.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/3096a8deace92d7df98c206c233bcf3f62c7e805/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/3332157790

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/63bb253cf3ea3c8d75c1d2600670c1f130fe5f92/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/63bb253cf3ea3c8d75c1d2600670c1f130fe5f92}{SORTEE-Github-Hackathon/manuscript@63bb253}
on October 26, 2022.

@@

GitHub limits committed file sizes to 100 Mb (megabytes \emph{About Large Files on GitHub} (\protect\hyperlink{ref-1Co6ZZjF1}{n.d.})), which can make it challenging for centralizing research compendia containing larger file sizes.
Users may still version large files using Git Large File Storage (\protect\hyperlink{ref-11GtZ7icJ}{\emph{Git Large File Storage}, n.d.}) text pointers, but may have to rely on external file storage alternatives (such as local or cloud-hosting).

@@

Modern research in ecology and evolution is highly collaborative, bringing together multidisciplinary teams from various institutions (\protect\hyperlink{ref-1HhzKAC1K}{Goring et al., 2014}).
On GitHub, collaborators can share feedback, brainstorm ideas, and troubleshoot problems (Figure \ref{fig:github-diagram}).
Project management can happen via three GitHub repository features: ``Issues'', ``Discussion'' and ``Projects''.
Github Issues allow for discrete tasks and sub-tasks to be identified, assigned to team members, and categorized with custom labels.
Github Discussions serve as a message board for conversation.
Finally, GitHub Projects integrate issues and pull requests on automated spreadsheets and project boards, providing users with real-time tracking of project priorities and status (\protect\hyperlink{ref-RhBKe0MG}{\emph{About Projects}, n.d.}).
Scripts, commit messages, and pull requests can be linked directly to issues, discussions, and projects providing a clear record of project workflow.
For instance, one can create a discussion on a project repository to decide which method to apply for biodiversity data analysis.
Then, an issue can be created to establish steps and responsibilities including data formatting, statistical analyses, figure generation, and issue resolution {[}\emph{e.g.}, see issues and discussions in the sPlotOpen {[}doi:10.1111/geb.13346{]} manuscript repository (\url{https://github.com/fmsabatini/sPlotOpen_Manuscript/issues?q=is\%3Aissue+is\%3Aclosed}){]}.
Using GitHub for all project-related conversation and planning, rather than email or messaging tools, makes it easier to keep track of progress throughout the lifespan of a project.
Unlike emails and messages which can get lost as more new tasks arise, GitHub issues are intentionally closed by repository administrators hiding the issue from view (closed issues remain accessible but not immediately visible).
Project management in GitHub can also be integrated with third-party applications, such as Zenhub (\url{https://www.zenhub.com}) or Slack (\url{https://slack.github.com}).
Zenhub allows for the enhanced visualization and organization of repositories and their issues, while the GitHub for Slack integration allows notifications from GitHub events to be sent directly to users or group channels (\protect\hyperlink{ref-1GRWGlDWy}{Slack, n.d.}).

@@

Making presentations, syllabi and other course materials can be done through most major high-level programming languages such as R, with \texttt{RMarkdown} (\protect\hyperlink{ref-QqMezOMg}{Xie et al., 2019}), Python, with \texttt{python-ppt} (\url{https://python-pptx.readthedocs.io}), and Julia, with \texttt{Remark.jl} (\url{https://juliapackages.com/p/remark}), and be version-controlled and stored in GitHub.
Once content is made, hosting a course website can be done through GitHub Pages (\protect\hyperlink{ref-MDQfMwCW}{\emph{Quickstart for GitHub Pages}, n.d.}) (\emph{e.g.}, \url{https://github.com/topics/course-website}).
This way, course content can be available to enrolled students, as well as a global pool of learners and teachers interested in the material.
Content can then be delivered via the course website, and/or a GitHub Organization with, for example, template repositories for assignments.
Student submissions are perhaps the most challenging component, but the new GitHub Classroom tool (\url{https://classroom.github.com}) allows instructors to host private assignments to be submitted collaboratively or individually as code or PDF files, and even build autograding tests.
Although time-consuming to establish, using these features can integrate learning version control and GitHub with the learning course content, and thus boost students' feelings of self-efficacy and confidence (\protect\hyperlink{ref-dqrFjoSb}{Trujillo \& Tanner, 2014}).

@@

\leavevmode\vadjust pre{\hypertarget{ref-11GtZ7icJ}{}}%
\emph{Git Large File Storage}. (n.d.). Git Large File Storage. Retrieved October 26, 2022, from \url{https://git-lfs.github.com/}

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-MDQfMwCW}{}}%
\emph{Quickstart for GitHub Pages}. (n.d.). GitHub Docs. Retrieved October 26, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/pages/quickstart}

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/3096a8deace92d7df98c206c233bcf3f62c7e805/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/3096a8deace92d7df98c206c233bcf3f62c7e805}{SORTEE-Github-Hackathon/manuscript@3096a8d}
on October 26, 2022.

@@

GitHub limits committed file sizes to 100 Mb (megabytes) (\protect\hyperlink{ref-1Co6ZZjF1}{\emph{About Large Files on GitHub}, n.d.}), which can make it challenging for centralizing research compendia containing larger file sizes.
Users may still version large files using Git Large File Storage (\url{https://git-lfs.github.com}) text pointers, but may have to rely on external file storage alternatives (such as local or cloud-hosting).

@@

Modern research in ecology and evolution is highly collaborative, bringing together multidisciplinary teams from various institutions (\protect\hyperlink{ref-1HhzKAC1K}{Goring et al., 2014}).
On GitHub, collaborators can share feedback, brainstorm ideas, and troubleshoot problems (Figure \ref{fig:github-diagram}).
Project management can happen via three GitHub repository features: ``Issues'', ``Discussion'' and ``Projects''.
Github Issues allow for discrete tasks and sub-tasks to be identified, assigned to team members, and categorized with custom labels.
Github Discussions serve as a message board for conversation.
Finally, GitHub Projects integrate issues and pull requests on automated spreadsheets and project boards, providing users with real-time tracking of project priorities and status (\protect\hyperlink{ref-RhBKe0MG}{\emph{About Projects}, n.d.}).
Scripts, commit messages, and pull requests can be linked directly to issues, discussions, and projects providing a clear record of project workflow.
For instance, one can create a discussion on a project repository to decide which method to apply for biodiversity data analysis.
Then, an issue can be created to establish steps and responsibilities including data formatting, statistical analyses, figure generation, and issue resolution (\emph{e.g.}, see issues and discussions in the sPlotOpen manuscript repository \protect\hyperlink{ref-doi:10.1111ux2fgeb.13346}{\textbf{doi:10.1111/geb.13346?}}); \emph{Issues · Fmsabatini/sPlotOpen\_Manuscript} (\protect\hyperlink{ref-3UAritXO}{n.d.})=is\%3Aissue+is\%3Aclosed{]}.
Using GitHub for all project-related conversation and planning, rather than email or messaging tools, makes it easier to keep track of progress throughout the lifespan of a project.
Unlike emails and messages which can get lost as more new tasks arise, GitHub issues are intentionally closed by repository administrators hiding the issue from view (closed issues remain accessible but not immediately visible).
Project management in GitHub can also be integrated with third-party applications, such as Zenhub (\url{https://www.zenhub.com}) or Slack (\url{https://slack.github.com}).
Zenhub allows for the enhanced visualization and organization of repositories and their issues, while the GitHub for Slack integration allows notifications from GitHub events to be sent directly to users or group channels (see \protect\hyperlink{ref-1GRWGlDWy}{Slack, n.d.}).

@@

Making presentations, syllabi and other course materials can be done through most major high-level programming languages such as R, with \texttt{RMarkdown} (\protect\hyperlink{ref-QqMezOMg}{Xie et al., 2019}), Python, with \texttt{python-ppt} (\url{https://python-pptx.readthedocs.io}), and Julia, with \texttt{Remark.jl} (\url{https://juliapackages.com/p/remark}), and be version-controlled and stored in GitHub.
Once content is made, hosting a course website can be done through GitHub Pages (\url{https://pages.github.com}; \emph{e.g.}, \url{https://github.com/topics/course-website}).
This way, course content can be available to enrolled students, as well as a global pool of learners and teachers interested in the material.
Content can then be delivered via the course website, and/or a GitHub Organization with, for example, template repositories for assignments.
Student submissions are perhaps the most challenging component, but the new GitHub Classroom tool (\url{https://classroom.github.com}) allows instructors to host private assignments to be submitted collaboratively or individually as code or PDF files, and even build autograding tests.
Although time-consuming to establish, using these features can integrate learning version control and GitHub with the learning course content, and thus boost students' feelings of self-efficacy and confidence (\protect\hyperlink{ref-dqrFjoSb}{Trujillo \& Tanner, 2014}).

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-3UAritXO}{}}%
\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved October 26, 2022, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}

@@
